---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-"
  # out.width = "100%"
)
library(nomnoml)
# knitr::knit_engines$set(nomnoml = nomnoml:::knit_nomnoml)
```

# nomnomlgraph

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->


The goal of `nomnomlgraph` is to enable the creation of basic diagrams such as those created with [nomnoml](https://nomnoml.com/) without having to familiarise with its syntax.

To create a `nomnoml` diagram with `nomnomlgraph` you will need two data frames: one with *nodes*, the other with *edges*, in line with the structure of data tyipically used to generate network graphs.

This facilitates cooperation across teams with members that may be intimidated by `nomnoml` syntax and will feel at home in front of a spreadsheet, or even as a shared spreasheet on Google Drive.


## Installation

You can install the development version of `nomnomlgraph` from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("giocomai/nomnomlgraph")
```

or from R universe:

``` r
install.packages('nomnomlgraph', repos = c('https://giocomai.r-universe.dev', 'https://cloud.r-project.org'))
```

## How to use

First, you will need a data frame with nodes:

```{r nodes}
library("nomnomlgraph")
nodes <- tibble::tribble(
  ~id, ~text,
  1, "Starting point",
  2, "Other starting point",
  3, "This is where things merge",
  4, "This is where things go"
)
knitr::kable(nodes)
```

Then one with edges:

```{r edges}
edges <- tibble::tribble(
  ~from, ~to, ~association,
  1, 3, "-",
  2, 3, "-",
  3, 4, "->"
)

knitr::kable(edges)
```

Et voilà:

```{r basic_nomnoml, eval = FALSE, echo=TRUE}
nn_graph(
  nodes = nodes,
  edges = edges
)
```

```{r basic_nomnoml_hidden, eval = TRUE, include=TRUE, echo = FALSE}
nn_graph(
  nodes = nodes,
  edges = edges,
  width = 400,
  height = 200,
  svg = TRUE
)
```

To which you can add a bunch of customisations, see `?nn_graph()` for details. E.g. 

```{r custom_nomnoml, eval = FALSE}
nn_graph(
  nodes = nodes,
  edges = edges,
  fill = "#fdf6e3",
  edgesStyle = "rounded",
  font = "Roboto Condensed",
  fillArrows = "true",
  svg = TRUE
)
```

```{r custom_nomnoml_hidden, eval = TRUE, echo = FALSE}
nn_graph(
  nodes = nodes,
  edges = edges,
  fill = "#fdf6e3",
  edgesStyle = "rounded",
  font = "Roboto Condensed",
  fillArrows = "true",
  width = 400,
  height = 200,
  svg = TRUE
)
```


## Something a bit more complex?


```{r nodes_more}
library("nomnomlgraph")
nodes <- tibble::tribble(
  ~id, ~text, ~classifier,
  1, "Partner X", "actor",
  2, "Partner Y", "actor",
  3, "Partner Z", "actor",
  4, "Initiator", "sender",
  5, "Do something together", "",
  6, "Quality control", "choice",
  7, "Additional fixes", "",
  8, "Launch!", "transceiver"
)
knitr::kable(nodes)
```

Then one with edges:

```{r edges_more}
edges <- tibble::tribble(
  ~from, ~to, ~association,
  4, 5, "-",
  1, 5, "-",
  2, 5, "-",
  3, 5, "-",
  5, 6, "->",
  6, 7, "No ->",
  7, 6, "-->",
  6, 8, "Yes! ->"
)

knitr::kable(edges)
```


```{r diagram_with_more}
nn_graph(
  nodes = nodes,
  edges = edges,
  edgesStyle = "rounded",
  font = "Roboto Condensed",
  svg = TRUE,
  width = 600,
  height = 300,
)
```

## Finalise on nomnoml.com

If you enable set the "output" parameter to "code", you will get a chunk of text that you can paste directly [on nomnoml.com](https://nomnoml.com/#view/%23direction%3A%20down%0A%23edges%3A%20rounded%0A%23lineWidth%3A%201%0A%23fill%3A%20%23FEFEFF%0A%23zoom%3A%204%0A%23arrowSize%3A%201%0A%23bendSize%3A%200.3%0A%23gutter%3A%205%0A%23edgeMargin%3A%200%0A%23fillArrows%3A%20false%0A%23font%3A%20sans%0A%23fontSize%3A%2012%0A%23leading%3A%201.25%0A%23padding%3A%208%0A%23spacing%3A%2040%0A%23stroke%3A%20%2333322E%0A%23title%3A%20filename%0A%0A%5B%3Csender%3EInitiator%5D-%5BDo%20something%20together%5D%0A%5B%3Cactor%3EPartner%20X%5D-%5BDo%20something%20together%5D%0A%5B%3Cactor%3EPartner%20Y%5D-%5BDo%20something%20together%5D%0A%5B%3Cactor%3EPartner%20Z%5D-%5BDo%20something%20together%5D%0A%5BDo%20something%20together%5D-%3E%5B%3Cchoice%3EQuality%20control%5D%0A%5B%3Cchoice%3EQuality%20control%5DNo%20-%3E%5BAdditional%20fixes%5D%0A%5BAdditional%20fixes%5D--%3E%5B%3Cchoice%3EQuality%20control%5D%0A%5B%3Cchoice%3EQuality%20control%5DYes!%20-%3E%5B%3Ctransceiver%3ELaunch!%5D) for further adjustments. 

```{r nn_code}
nn_graph(
  nodes = nodes,
  edges = edges,
  output = "code",
  edgesStyle = "rounded"
) |>
  cat()
```


(remember to use `cat()` if you are copy/pasting it from the console to process the new lines)


## More

For more details, see the documentation of the `nomnoml` package for R: https://github.com/rstudio/nomnoml/

The original nomnoml: https://nomnoml.com/


## Licensing

This package is distributed under the MIT license. 
